# Communicable, Maternal, Neonatal, and Nutritional Disease Burden (CMNN)

```{r}
# Load necessary packages
pacman::p_load(tidyverse, knitr, here, janitor,esquisse)

# Import the communicable diseases data
data_cmnn <- read_csv(here("data", "burden-of-disease-cmnn.csv"))
data_cmnn
```

## Table of Estimates for CMNN Burden Over Time

```{r}
# Here render a table for the DALY burden over time for the three countries
three_counteries<-data_cmnn %>% filter(Entity==c("America","Andorra","Algeria")) %>% tabyl(Entity, Year)
# You should pivot the data to show each country in a separate column.

pivoted_data <- pivot_longer(three_counteries, cols = -Entity, names_to = "Year", values_to = "Value")
table<-kable(pivoted_data)
table
# Use kable() from the knitr package to render the table.
```

## Plot Showing Trends in CMNN Burden Over Time

```{r}
# Here, plot a line graph showing the trend of DALY burden for the chosen countries over time. You can use ggplot2 to create this plot. Each country's line should be a different color.

ggplot(pivoted_data) +
  aes(x = Entity, y = Value, fill = Year) +
  geom_col() +
  scale_fill_hue(direction = 1) +
  theme_minimal()

```

## Summary of CMNN Burden Findings

Provide a brief analysis based on the data presented in the table and chart. Highlight any significant findings or patterns. About 3 sentences.
DALYS is higher for Algeria than America and Andorra

